---
title: "R For Data Science-Assignment-3"
author: "RAGU J"
date: "2022-11-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
install.packages("tidyverse")
library(tidyverse)
```

```{r}
library(nycflights13)
```


```{r}
```

##Question-1
A. Compare and contrast the following operations on a data.frame and equivalent tibble. What is different? Why might the default data frame behaviors cause you frustration?
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x
#> [1] "a"
df[, "xyz"]
#> [1] "a"
df[, c("abc", "xyz")]
#>   abc xyz

```
##Answer
    When using the $ operator, data frames will select any column that begins with the first letter. So in the Given example, there is no column “x”, but because there is a column “xyz” - the data frame pulls the corresponding rows for that column. 
   The frustration is because in some situations a data frame will returns a different thing like in the last two previous lines of code. Tibble will return the same thing, providing consistency.


B.What option controls how many additional column names are printed at the footer of a tibble?
##Answer

   By default, information of all remaining columns are printed at the footer. To limit the number of additional column information, we can use the argument "n_extra." 
##For exampe:
```{r}
print(nycflights13::flights, n_extra = 2)
```

##Question-2:
Generate the correct format string to parse each of the following dates and times:
d1 <- "January 1, 2010"
d2 <- "2015-Mar-07"
d3 <- "06-Jun-2017"
d4 <- c("August 19 (2015)", "July 1 (2015)")
d5 <- "12/30/14" # Dec 30, 2014
t1 <- "1705"
t2 <- "11:15:10.12 PM"
##Answer
```{r}
parse_date(d1, "%B %d, %Y")

parse_date(d2, "%Y-%b-%d")

parse_date(d3, "%d-%b-%Y")

parse_date(d4, "%B %d (%Y")
           
parse_date(d5, "%m/%d/%y")

parse_time(t1, "%H%M")


```



##Question-3:
Practice referring to non-syntactic names in the following data frame by: 
```{r}
annoying <- tibble( 
`1` = 1:10, 
`2` = `1` * 2 + rnorm(length(`1`)) )

```

a. Extracting the variable called 1. 
##Answer
```{r}
annoying[["1"]]
##or
annoying$`1`
```
b. Plotting a scatterplot of 1 versus 2.
##Answer
```{r}
ggplot(annoying, aes(x = `1`, y = `2`)) +
  geom_point()
```
c. Creating a new column called 3, which is 2 divided by 1. 
##Answer
```{r}
annoying[["3"]] <- annoying[["2"]] / annoying[["1"]]

annoying$`3`
```
d. Renaming the columns to one, two, and three: 
##Answer
```{r}
annoying <- rename(annoying, one = `1`, two = `2`, three = `3`)
glimpse(annoying)

```



4.	Identify what is wrong with each of the following inline CSV files. 
What happens when you run the code? 
read_csv("a,b\n1,2,3\n4,5,6") 
read_csv("a,b,c\n1,2\n1,2,3,4")
read_csv("a,b\n\"1") 
read_csv("a,b\n1,2\na,b")
read_csv("a;b\n1;3")
##Answers
```{r}
read_csv("a,b\n1,2,3\n4,5,6") 
```
Only two columns are specified in the header "a" and "b", but the rows have three columns, so the last column is dropped.

```{r}
read_csv("a,b,c\n1,2\n1,2,3,4")
```
The numbers of columns in the data do not match the number of columns in the header

In row one, there are only two values, so column "c" is set to missing.

In row two, there is an extra value, and that value is dropped.
```{r}
read_csv("a,b\n\"1") 
```

The opening quote " "1 " is dropped because it is not closed, and "a" is treated as an integer.
```{r}
read_csv("a,b\n1,2\na,b")
```

Both "a" and "b" are treated as character vectors since they contain non-numeric strings.

This may have been intentional, or the author may have intended the values of the columns to be "1,2" and "a,b".

```{r}
read_csv("a;b\n1;3")
```
The values are separated by ";" rather than ",".
