---
title: "R for Data Science-Assignment-5"
author: "RAGU J"
date: "2022-11-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(lubridate)
library(nycflights13)
```
##Question-1

Construct regular expressions to match words that: 

a. Start and end with the same character. 

```{r}
str_view(words, "(.).*\\1$", match = TRUE)
```
b. Contain a repeated pair of letters (e.g., “church” contains “ch” repeated twice). 

```{r}
str_view(words, "(..).*\\1", match = TRUE)
```

c. Contain one letter repeated in at least three places (e.g., “eleven” contains three “e”s).

```{r}
str_view(words, "(.).*\\1.*\\1", match = FALSE)
```


##Question-2
How would you match the sequence "'\?
##Answer

```{r}
x <- "a \"'\\b"
writeLines(x)

str_view(x, "\"'\\\\")
```

##Question-3
Use the appropriate lubridate function to parse each of the following dates: 
d1 <- "January 1, 2010"
 d2 <- "2015-Mar-07"
 d3 <- "06-Jun-2017" 
d4 <- c("August 19 (2015)", "July 1 (2015)") 
d5 <- "12/30/14" # Dec 30, 2014

```{r}
d1 <- "January 1, 2010"
 d2 <- "2015-Mar-07"
 d3 <- "06-Jun-2017" 
d4 <- c("August 19 (2015)", "July 1 (2015)") 
d5 <- "12/30/14" 

#ANSWER
mdy(d1)
ymd(d2)
dmy(d3)
mdy(d4)
mdy(d5)
```

##Question-4
What happens if you parse a string that contains invalid dates? 
ymd(c("2010-10-10", "bananas"))

##Answer
  It shows a warning message and print "NA" instead of "bananas"(Warning:  1 failed to parse.[1] "2010-10-10" NA     )

```{r}
ymd(c("2010-10-10", "bananas"))
```


