---
title: "Assignment-II"
author: "RAGU J"
date: "2022-11-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```


```{r}
install.packages("nycflights13")
install.packages("tidyverse")
library(nycflights13)
library(tidyverse)

```
1.	Sort flights to find the fastest flights

Answer:
```{r}
arrange(flights,air_time)
```

2.	Compare dep_time, sched_dep_time, and dep_delay. How would you expect those three numbers to be related?


Answer:
 I would expect that is "dep_delay" is equal to the difference between "sched_dep_time" and "dep_time"


```{r}
select(flights,dep_time,sched_dep_time,dep_delay)
```

3.	Brainstorm at least 5 different ways to assess the typical delay characteristics of a group of flights. Consider the following scenarios:


  a.	A flight is 15 minutes early 50% of the time, and 15 minutes late 50% of the time.

  b.	A flight is always 10 minutes late.


  c.	A flight is 30 minutes early 50% of the time, and 30 minutes late 50% of the time.

  d.	99% of the time a flight is on time. 1% of the time it’s 2 hours late
Ans:
```{r}

not_cancelled <- flights %>%
  filter(!is.na(air_time))
###Arrival Time is More Important so sort that first
not_cancelled %>%
  group_by(tailnum) %>%
  mutate(
    count = n(),
    median_arr_delay = median(arr_delay),
    median_dep_delay = median(dep_delay)
  ) %>%
  filter(count > 30) %>%
  arrange(median_arr_delay, median_dep_delay)


###More than 10 mins Late
not_cancelled %>%
  group_by(tailnum, origin, dest) %>%
  summarise(
    count = n(),
    arr_delay_10_c = sum(arr_delay > 10),  
    arr_delay_10_p = mean(arr_delay > 10),  
    dep_delay_10_c = sum(dep_delay > 10),
    dep_delay_10_p = mean(dep_delay > 10)  
    ) %>%
  filter(count > 20) %>%
  arrange(desc(arr_delay_10_p))


### Best flights under 30 mins early or late criteria sorted 
not_cancelled %>%
  group_by(tailnum) %>%
  mutate(
    count = n(),
    arr_30_early = mean(arr_delay < -30),
    dep_30_early = mean(dep_delay < -30),
    arr_30_late  = mean(arr_delay > 30),
    dep_30_late = mean(dep_delay > 30)
  ) %>%
  filter(count > 20) %>%
  arrange(desc(arr_30_early), desc(dep_30_early), arr_30_late, dep_30_late) %>%
  select(dest)
```
      According to the scenarios and coding ,departure delay is important



4.	Which plane (tailnum) has the worst on-time record?
Answer:
```{r}
select(flights,desc(arr_delay),desc(dep_delay))
```



5.	Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.

Answer:
```{r}
select(flights,dep_time,dep_delay,arr_time,arr_delay)
select(flights,4,6,7,9)
select(flights,starts_with("dep_"),starts_with("arr_"))
select(flights, "dep_time", "dep_delay", "arr_time", "arr_delay")



```

