---
Title: "R FOR DATA SCIENCE"
Author: "RAGU J    rf59:06 AM 11/10/20226]
"999
Date: "27/09/2022"
Output: html_document
Editor_options: 
  markdown: 
    wrap: 72
---

### ASSIGNMENT QUESTIONS AND SOLUTIONS

#### Introduction Exercises:

library(ggplot2)

```{r}
```

##question 1

What happens if you make a scatterplot of class versus drv? Why is theplot not useful?
##Answer-1
```{r}
 ggplot(mpg, aes(x=class,y=drv))+
          geom_point()

```

##question 2

What's gone wrong with this code? Why are the points not blue?
ggplot(data = mpg) + geom_point(aes(x = displ,y = hwy, color = "blue"))
##Answer-2
 The points are not blue because the perameter color is included with aesthetic. if color is placed outside displays the points in blue color

```{r}
ggplot(data = mpg) + 
   geom_point(aes(x = displ,y = hwy), color = "blue")

```

##question 3

a)  What happens if you map a aesthetic to something other than a variable name,like aes(colour = displ\<5)?
##Answer-3
```{r}

ggplot(data=mpg)+
    geom_point(mapping = aes(x=displ,y=hwy,color=displ<5))

```

b)  What does the stroke aesthetic do? What shapes does it work with?

```{r}
ggplot(data=mpg)+
    geom_point(aes(x=displ,y=hwy,stroke=3))

```
  Stroke is used to adjust the border size for shapes. it work withpoints(geom_point)shape.

##question 4

Read? Facet_wrap. What does nrow do? What does ncol do? What otheroptions control the layout of the individual panels? Why doesn'tfacet_grid() have nrow and ncol variables?
##Answer-4
  1.The arguments nrow (ncol) determines the number of rows (columns) to use when laying out the facets. It is necessary since facet_wrap() onlyfacets on one variable.
  2.The nrow and ncol arguments are unnecessary for facet_grid() since the number of unique values of the variables specified in the function determines the number of rows and columns.

##question 5

a)  What plots does the following code make? What does . do?
##Answer-5
```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)

```

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)

```

b)  When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?

  There will be more space for columns if the plot is laid out
horizontally (landscape)

##question 6

What geom would you use to draw a line chart? A boxplot? A histogram? An
area chart?
##Answer-6
 Line_chart:geom_line() box_plot:geom_boxplot()
histogram:geom_histogram() area_chart:geom_area()

##question 7

Will these two graphs look different? Why/why not?

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_point() +
geom_smooth()

```
```{r}
ggplot() +
geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))

```
##Answer-7
 No,the two graphs looks similar.because both geom_point() and
geom_smooth() use same data and mappings

##question 8

What does geom_col() do? How is different to geom_bar()?
##Answer-8
 The geom_col() function has different default stat than geom_bar().

1. The default stat of geom_col() is stat_identity(), which leaves the data as is. The geom_col() function expects that the data contains x values and y values which represent the bar height.

2. The default stat of geom_bar() is stat_count(). The geom_bar() functionaly expects an x variable. 
 
3. The stat, stat_count(), pre processes input data by counting the number of observations for each value of x. The y
aesthetic uses the values of these counts.

##question 9

What is the default geom associated with stat_summary()? How could yourewrite the previous plot to use that geom function instead of the stat
function?

## Answer-9
    The default geometry associater with stat_summary() is geom_pointrange(). 
```{r}
ggplot(data =diamonds) + geom_pointrange(mapping = aes(x=cut,y=depth),stat ="summary" ,fun.ymin = min,fun.ymax =max,fun.y = mean)

```

##question 10

What does the plot below tell you about the relationship between city
and highway mpg? Why is coord_fixed() important? What does geom_abline()
do?

```{r}
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()

```
